% Thesis Supervised Section
\begin{rubric}{Thesis Supervised}

\subrubric{Ph.D. Ongoing}
\entry*{} \textbf{Saurabh Maurya (2025--Ongoing):} Air Pollution and Crop Yield.
\entry*{} \textbf{Vineet Jain  (2025--Ongoing):} Pollution Dispersion in ground Water.

\entry*{} \textbf{Maniranjan (2022--Ongoing):} Comprehensive Assessment of Groundwater in Tropical River Basins using Machine Learning and SWAT Model.

\entry*{} \textbf{Megavath Narahari (2021--Ongoing):} Effects of Climate Change on Water Quality.

\entry*{} \textbf{Krishna Kumar (2022--Ongoing):} Crop Yield Estimation and Forecasting using Machine Learning.

\entry*{} \textbf{Hari Prakash (2023--Ongoing):} Peak Discharge Estimation for Ungauged Basins.

\entry*{} \textbf{Ashwin Chitravanshi (2023--Ongoing):} Water Quality Modeling for Varuna River Basin.



\subrubric{M.Tech Students}
\entry*{} \textbf{Ritika Upadhyay (2024-Ongoing):} Impact of Pollution on Rainfall Characteristics. \emph{Co-supervisor (External with BHU).}
\entry*{} \textbf{Makardhwaj Awasthi (2024-Ongoing):} Atmospheric–Rainfall Interaction Analysis. \emph{Co-supervisor (External with BHU).}
\entry*{} \textbf{Buddepu Harsha Vardhan (2023-2025):} A Comparative Evaluation of WRF and ANN for Weather Prediction: Performance and Accuracy.
\entry*{} \textbf{Saurabh Maurya (2023-2025):} Investigation of Microphysical Characteristics of Raindrop Size Distribution using WRF Model.
\entry*{} \textbf{Raju Singh (2023-2025):} Estimation of Surface Velocity in Open Channel Flows using Image Processing.
\entry*{} \textbf{Shailesh Kushwaha (2023-2025):} Seasonal Forecasting of Crop Yield over Varuna River Basin.
\entry*{} \textbf{Tripti Yadav (2023-2025):} Estimation of E-Flow for Varuna River Basin.
\entry*{} \textbf{Ritika Upadhyay (2025):} Impact of Pollution on Rainfall Characteristics (Tentative). \emph{Co-supervisor (External with BHU).}
\entry*{} \textbf{Makardhwaj Awasthi (2025):} Atmospheric--Rainfall Interaction Analysis (Tentative). \emph{Co-supervisor (External with BHU).}
\entry*{} \textbf{Suryansh Srivastava (2025):} Geomorphological Change Analysis using Arc-GIS (Tentative). \emph{Co-supervisor (External with BHU).}
\entry*{} \textbf{Shadab Ansari (2020):} Single and Dual Frequency Atmospheric Free Precise Point Positioning using Combined GPS and GLONASS Observations.
\entry*{} \textbf{Prity Dhanai (2021):} Rainfall Triggered Slope Instability Analysis with Changing Climate.
\entry*{} \textbf{Pankaj Singh (2021):} Spatiotemporal Prediction of Criteria Air Pollutants using Air Pollution Monitoring Station Data.
\entry*{} \textbf{Shubham Khare (2022):} Effects of COVID-19 Lockdown on Meteorological Variables over India.
\entry*{} \textbf{Anandita Raj (2022):} Impacts of Climate Change on Water Quality for Krishna River Basin.

\subrubric{B.Tech Students}


\entry*{} \textbf{Harshit Patel (24065047) (2025-26):} Dam Break Analysis using HEC-RAS.

\entry*{} \textbf{Abhyudaya Singh (24065008) (2025-26):} Inland River Water Quality Modeling.

\entry*{} \textbf{Ketan Kumar (24065055) (2025-26):} Water Quality Analysis using HEC-RAS.

\entry*{} \textbf{Gautam Kumar (24065040) (2025-26):} Bridge Scour Analysis using HEC-RAS.

\entry*{} \textbf{Aryan Gupta (24065026) (2025-26):} 2D Sediment Transport Modelling of the Ganga River at Varanasi using HEC-RAS 6.6.

\entry*{} \textbf{Narendra Prasad (22065058) (2025-26):} CFD Modeling of Bridge Pier Scour.

\entry*{} \textbf{Arushi Aggarwal (23064002) (2025-26):} Geomorphological Analysis.

\entry*{} \textbf{Abhishek Sharma (23065006) (2025-26):} Forecasting of River Sinuosity using Remote Sensing and Machine Learning.

\entry*{} \textbf{Bishal Das (23065032) (2025-26):} DSSAT Crop Simulation.

\entry*{} \textbf{Chandraveer Singh (23065035) (2025-26):} Forecasting of River Sinuosity using Remote Sensing and Machine Learning.

\entry*{} \textbf{Vaibhav Rajvardhan (23065110) (2025-26):} 2D Hydraulic Simulation and Inundation Mapping of the Hirakud Dam Breach.

\entry*{} \textbf{Mayank Singh (23065124) (2025-26):} Sub-daily Rainfall Analysis over Varuna River Basin.
\entry*{} \textbf{Nitish Kumar Maurya (20065067), Umesh Harsana (20065109) (2024-25):} River Meandering Analysis Project.
\entry*{} \textbf{Dinesh Singh (20065035), Harshit Bangari (20065041), Bhuvnesh Gaur (20065030) (2024-25):} Flood Risk Zone Mapping using ArcGIS.
\entry*{} \textbf{Mayank Mani Nath Gupta (21065127) (2024-25):} River Extraction using Image Processing and QGIS using Python.
\entry*{} \textbf{Saatwiik Srivastava (21065091) (2024-25):} Rainfall--Runoff Modeling using ANN.
\entry*{} \textbf{Vishal Yadav (21065113) (2024-25):} River Boundary Extraction using Image Processing and QGIS.
\entry*{} \textbf{Aditi Gupta (21065006) (2024-25):} Monthly Discharge Estimation using Image Processing.
\entry*{} \textbf{Shridhar Kumar (21065100) (2024-25):} Application of ANN in Rainfall--Runoff Modeling.
\entry*{} \textbf{Aman Mani Shandilya (22065012) (2025):} River Extraction and Analysis using Image Processing and QGIS.
\entry*{} \textbf{Sanyam Jain (22065118) (2025):} Application of ANN in Rainfall--Runoff Modeling.
\entry*{} \textbf{Harsh Pant (22065128), Aditya Maurya (22065122) (2025):} Analysis of NCEP Global Forecast Data.
\entry*{} \textbf{Chandraveer Singh (23065035) (2025):} Topic under progress.
\entry*{} \textbf{Danish Dubey (23065038) (2025):} CFD Modeling of Varuna River Basin.
\entry*{} \textbf{Harsh Suryawanshi (23065051) (2025):} Impact of Climate Change on Water Footprint and Crop Yield over Mahanadi Basin, Odisha.
\entry*{} \textbf{Sachin (23065092) (2025):} Impact of Climate Change on Water Footprint and Crop Yield over Mahanadi Basin, Odisha.
\entry*{} \textbf{Vaibhav Rajvardhan (23065110) (2025):} Impact of Climate Change on Water Footprint and Crop Yield over Mahanadi Basin, Odisha.
\entry*{} \textbf{Mahesh Chandra Verma, Nishant Rai, Balram Yogi, Kuldeep Bhamu (2020):} Impact of Climate Change on Water Resources using Artificial Neural Network (ANN).
\entry*{} \textbf{Anitya Sagar, Pulkit Garg, Abhay Singh, Umesh Karna (2021):} Design of Rainwater Harvesting Structure for MNNIT Allahabad Campus.
\entry*{} \textbf{Shiv Virendra Chaubey, Ajit Kumar, Aditya Kumar, Shubham Kumar Singh (2022):} Impact of Climate Change on Water Footprint and Crop Yield over Mahanadi Basin, Odisha.

\subrubric{External Thesis (BITS Pilani)}

\entry*{} \textbf{Nimish Tiwari (2022A2PS1449H) (2026):} Prediction of Water Quality Parameters of the Varuna River Basin using Remote Sensing and Machine Learning. \emph{Co-supervisor with Prof. Abhradeep Majumder (BITS Pilani).}
\end{rubric}